{\fontfamily{ptm}\selectfont A Proximal Point framework of Nesterov type accelerated gradient}

### 2024-08-20 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, a lot of updates to the notes

        \par
        However, the construction exhibits variations for different variants of the accelerated gradient algorithm. 
        A different construction of $\phi_k$ yield a different algorithm. 
        As shown in Nesterov's book \cite*[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence: 
        \begin{align*}
            \phi_0 (x) &= f(x_0) + \frac{\gamma_0}{2}\Vert x - x_0\Vert^2
            \\
            l_f(x; y_k) &= f(\mathcal T_Ly_k) + 
            \frac{1}{2L}\Vert \mathcal G_L(y_k)\Vert^2 + 
            \langle \mathcal G_L(y_k), x - y_k\rangle + 
            \frac{\mu}{2}\Vert x - y_k\Vert^2
            \\
            \phi_{k + 1}(x) &= 
            (1 - \alpha_k)\phi_k + 
            \alpha_k l_f(x; y_k), 
        \end{align*}
        Here, $\mathcal G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$. Finally, with $\mu = 0$, it reduces to ineuality appeared in 
        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.

@@

\printbibliography

>>>>

        \par
        However, the construction exhibits variations for different variants of the accelerated gradient algorithm. 
        A different construction of $\phi_k$ yield a different algorithm. 
        As shown in Nesterov's book \cite[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence:

        \begin{align*}
            \phi_0 (x) &= f(x_0) + \frac{\gamma_0}{2}\Vert x - x_0\Vert^2
            \\
            l_f(x; y_k) &= f(\mathcal T_Ly_k) + 
            \frac{1}{2L}\Vert \mathcal G_L(y_k)\Vert^2 + 
            \langle \mathcal G_L(y_k), x - y_k\rangle + 
            \frac{\mu}{2}\Vert x - y_k\Vert^2
            \\
            \phi_{k + 1}(x) &= 
            (1 - \alpha_k)\phi_k + 
            \alpha_k l_f(x; y_k), 
        \end{align*}
        Here, $\mathcal G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$. Finally, with $\mu = 0$, it reduces to ineuality appeared in 
        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.

@@

\bibliographystyle{siam}
\bibliography{references/refs}
